The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
edits

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored. In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler satellite rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from a $\delta$~Scuti variable, as is seen in Figure~\ref{contamination}.

>>>>

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored. In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from a $\delta$~Scuti variable, as is seen in Figure~\ref{contamination}.
